\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel Space

### 2012-05-14 evaluation.tex
add one space

This bug was also found during grading, and took substantially less time to verify by hand than the previous bug. When a thread does \texttt{yield} to a specific other TID, the other thread's thread control block (TCB)is not protected between lookup-by-TID and yield-to. If that thread exits during that time, a use-after-free (and worse, a completely invalid schedule to a nonexistent thread) results.

>>>>

This bug was also found during grading, and took substantially less time to verify by hand than the previous bug. When a thread does \texttt{yield} to a specific other TID, the other thread's thread control block (TCB) is not protected between lookup-by-TID and yield-to. If that thread exits during that time, a use-after-free (and worse, a completely invalid schedule to a nonexistent thread) results.
